When are Fuzzy Extractors Possible?

### 2015-02-10 trunk/info-bounds/FuzzyExtPossibility.tex
revising proofs with new notation

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (\beta_{t,i}-1) /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 4$.

@@

\begin{proof}
We prove the stronger average case statement.
We first describe a family $\mathcal{W}_Z$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
Let $\mathcal{W}_Z$ be the set of all distributions of the form 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} w_1 + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{\gamma} \end{pmatrix} 
\]
The family is defined by the parameters $a_2,.., a_\gamma$ and $b_2,..., b_\gamma$ (seen by the adversary) and the distribution is sampled by sampling $w_1$.  Each distribution $W_z$ is an affine line in space $\mathbb{F}^\gamma$. The algorithm $\sketch, \rec$ never see $Z$ only the outcome of $v\leftarrow V$.
Fix some $4\le t < \gamma$.
We show the following~(in \apref{sec:proof secure sketch imposs}):

@@

Our counterexample uses a slightly different family of distributions $\mathcal{W}_Z$ than the counterexample for secure sketches.  
We will work over a binary alphabet~(we used a large alphabet in our counterexample for secure sketches).  A  property of the binary Hamming space is that a large fraction of any set of bounded size is the near ``boundary'' of that set.  This will be crucial in our proof.  We will embed the larger alphabet in the secure sketch counterexample into the binary Hamming metric.
Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} .
\]
The multiplication is in $\mathbb{F}$.  The family $\mathcal{W}_Z$ is parameterized by $z = a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$.  
A particular distribution $W_z$ is then the uniform distribution over choices of $x$.
 Define $V$ as the process of uniformly choosing $W_z\leftarrow \mathcal{W}_Z$ and then sampling from $w\leftarrow W_z$.  The adversary sees $\sketch(V)$  and $Z$.  We then show the following~(proofs in \apref{sec:fuzz ext proof}):
\begin{itemize}
\item \propref{prop:dist fuzzy ent fuzz}: for all $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z) = \omega (\log n)$. 
\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
\item \lemref{lem:fuzz can't get key}: In expectation across $Z$, a large subset of keys that are not possible.  In more detail,
\begin{itemize}
\item Half the keys have at most $2^{n- \kappa}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $\Key_{small}$.  
\item Consider some $\key \in \Key_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
Consider the set of $V_{\key } = \{w | \rep(w, p) = \key \}$.  All points in $V | \sketch(V)$ are distance $t$ from a boundary of $V_\key$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $\key$).  We show that most of $V_\key$ is near a boundary.  A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short}.  Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.  The number of $w$ that could produce $\key$ is small.
\item There are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).  Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_2$ have disjoint support outside of a single point $w$.
\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ contains at most one point~(the received point $v$).  Checking if $V|Z \cap V_{\key}$ is nonempty is an effective distinguisher.
\end{itemize}
\end{itemize}

@@

%\section{Leveraging convex combinations?}
%\label{sec:convex comb}
%\bnote{be careful uncommenting this, some notation may be out of date}
%In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.  For example, consider the following hypothetical extension to \consref{cons:universal hash}.  Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_\alpha$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.  However, the problem arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated. 
%
%We now describe a possible modification to the hashing construction.  Upon receiving an input $w$, sample a distribution $W_i$ from the set of distributions where $w$ has nonzero probability, write $i$ and perform the sketch as before for distribution $W_i$.  Intuitively, writing down a distribution $i$ should not do any harm as each of distributions $W_i$ has the same min-entropy as the starting distribution.  Unfortunately, this proposal may remove all entropy.  %Furthermore, each of these distributions is flat and thus, \consref{cons:universal hash} should apply.  However, this is not the case.
%
%%In the flat case, we used a hash whose length was proportional to the number of points in the largest ball.  The residual entropy in this case was within a superlogarithmic factor of $\Hfuzz(W)$.  However, in the setting where $W$ is a convex combination of flat sources this does not hold.
%
%Consider set of distributions $W_i$ where each $W_i$ has two components, first $W_i$ contains a distinguished point $w^*$ where $\Pr[W=w^*] = 2^{-k}$ and $w^*$ has no neighbors and $W_i$ contains a set $B_i$ of $2^{-k}-1$ points within distance $t$ each with probability $2^{-k}$.  This distribution is illustrated in \figref{fig:convex comb}.  
%
%\begin{figure}
%
%\centering
%    \includegraphics[width=.9\textwidth]{convexCombExample.png}
%    \caption{A convex combination of $W_1,..., W_\alpha$ has high min and fuzzy min-entropy, but sketching by using the component flat distributions removes all entropy.}
%\label{fig:convex comb}    
%\end{figure}
%
%
%The fuzzy min-entropy of $W_i$ is almost $0$ as the overwhelming majority of the probability space lies in $B_i$.  Now consider the distribution $W$ that is a convex combination of the $W_i$~(we assume that $B_i$ do not intersect).  Note that $\Hoo(W)=k$ and that $\Hfuzz(W)\approx \min\{\alpha, k\}$ where $\alpha$ is the number of distributions $W_1,..., W_\gamma$.  The value $\alpha$ may be quite large and $k$ may be the dominant factor.
%
%Consider an input point $w\in W$.  One of two cases occurs either $w=w^*$ or $w\in B_i$ for some $i$.  It should be clear in either case that the selected distribution $W_i$ is uniformly distributed from $\{1,..., \alpha\}$.  For any of the selected distributions, there is a ball with $\approx 2^{-k}$ points and thus the hash based construction must write down approximately $k$ points.  This means that $\Hav(W | \sketch(W))  = \Hav(W_i | \sketch(W_i)) \approx 0$.  This is despite the fact $\Hfuzz(W) \approx \min\{\gamma, k\}$.  Thus, the ability to sketch flat distributions does not easily admit a technique to sketch non-flat distributions.  
\bnote{I removed the discussion of convex combs for the submitted version}

\section{A Definitional Equivalence}
\label{sec:def equiv}
%We refer to $\mathcal{W}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular outcome taken $w\in W$ as the \emph{sample}.

As described in \secref{sec:family of dist}, our negative results rule out security for an average member of $\mathcal{W}$.  It may be possible to significantly improve parameters by only ruling out security for a single member $W$.

Recall the security game of a fuzzy extractor: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{W}$ 3) The challenger wins if $\Hav(W|\sketch(W))\ge \tilde{m}$.  Instead of just thinking of the uniform distribution over $\mathcal{W}$, consider an arbitrary distribution $V$ over elements of $\mathcal{W}$.  The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie} if $\mathcal{A}$ announces $V$ instead of a single element $W$.  That is, the following two player games have the same equilibrium:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{W}}_1(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W})$\\
$W \leftarrow \mathcal{A}(\mathcal{W}, \sketch, \rec)$\\
If $W\not\in \mathcal{W}$, $\mathcal{C}$ wins.\\
If $\Hav(W | \sketch(W))\ge \tilde{m}$, $\mathcal{C}$ wins.\\
Else $\mathcal{A}$ wins.
\end{tabbing} 
\vspace{.065in}
\end{minipage}  &
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{W}}_2(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
$V \leftarrow \mathcal{A}(\mathcal{W})$\\
$(\sketch, \rec)\leftarrow \mathcal{C}(V, \mathcal{W})$\\
$W \leftarrow V$\\
If $W\not\in \mathcal{W}$, $\mathcal{C}$ wins.\\
If $\Hav(W | \sketch(W))\ge \tilde{m}$, $\mathcal{C}$ wins.\\
Else $\mathcal{A}$ wins.
\end{tabbing}
\end{minipage}
\end{tabular}
\end{center}

%The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.  In $\Exp^{\mathcal{W}}_2$, the adversary specifies a distribution $V$ over sources, and the challenger then specifies their algorithm.  
This means that showing security for a family of distributions $\mathcal{W}$ is equivalent to showing security for all  distributions $V$ when the distribution is known to the algorithms $V$.  In our negative results, the adversary  uses the uniform distribution $V$ over $\mathcal{W}$.  However, it may be possible to improve parameters by using a different $V$. This would just rule out some member of $\mathcal{W}$ not an average member.  This is true for fuzzy extractors as well and is resilient to changes in parameters including imperfect correctness.

%Since the distribution used in our negative results was uniform it is stronger, ruling out security for an average $\mathcal{W}$.  However, constructing a nonuniform $V$ may improve these results.
%\begin{lemma}
%\label{lem:quant switch fuzz}
%Let $\mathcal{W}$ be a family of distributions.  If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.  Let $V$ be a distribution over $\mathcal{W}$.  Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.  If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
%\end{lemma}

%\begin{corollary}
%\label{cor:no fuzz for dist}
%Let $\mathcal{W}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
%\end{corollary}
%
%Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
\section{Fuzzy min-entropy}
\label{sec:proof fuzz necessary}
In this section, we provide proofs of the items in \secref{sec:minimal conditions}.  
\begin{proof}[Proof of \propref{prop:fuzz necessary}]
Let $W$ be a distribution where $\Hfuzz(W) = m$.  This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] = 2^{-m}$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $\key, p$.
\item If $\rep(w', p) = \key$, output $1$.
\item Else output $0$.
\end{itemize}
Clearly, $\Pr[D(\Key, P) = 1]\geq 2^{-m} - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus,
\[
\sd((\Key, P), (U_\kappa, P)) \ge \delta^D((\Key, P), (U_\kappa, P))\geq 2^{-m} -\delta -2^{-\kappa}.
\]
This completes the proof of \propref{prop:fuzz necessary}.
\end{proof}
\begin{proof}[Proof of \lemref{lem:conditional fuzz rule}]
\begin{align*}
\Hfuzz(W | P=p) &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \Pr[W=w | P=p] \right)\\
 &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w \wedge P=p]}{\Pr[P=p]} \right)\\
% &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
 &\ge -\log \left(\max_{w'}  \sum_{w\in W| \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
 &= \Hfuzz(W) + \log \Pr[P=p].
\end{align*}
This completes the proof of \lemref{lem:conditional fuzz rule}.
\end{proof}

@@

Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.  The size of $W^*$ is at most $\beta_{t,i}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  The probability that another element $w^*$ matches the hash is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{\beta_{t,i}-1}{|R_i|} = \delta
\end{align*}
The first inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.

@@

\begin{proposition} 
\label{prop:each element good} For each $W\in\mathcal{W}$, $\Hfuzz(W) = \omega(\log n)$.
\end{proposition}
\begin{proof}
Consider some $W\in\mathcal{W}$.  The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.  We now show that for any $w, w'\in W$, $\dis(w, w') = \gamma>t$.  This shows that $\Hfuzz(W) = \Hoo(W)$.  Fix some $w, w'\in W$.  Clearly, $w_1 \neq w_1'$, for any $i$, $w_i = a_i w_1 + b_i$ and $w_i' = a_i w_1' + b_i$.  Since $a_i\neq 0$, $a_iw_1 \neq a_iw_1'$ and thus $a_iw_1+b_i \neq a_iw_1'+b_i$.  That is, $\dis (w, w')  =\gamma$.
\end{proof}

\begin{proposition}
\label{prop:distribution uniform} $V$ is the uniform distribution over $\mathbb{F}^\gamma$.
\end{proposition}
\begin{proof}
Consider some $w\in V$.  Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.  The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\gamma$ are uniformly random.
\end{proof}

@@

By the Singleton bound, this implies that $H_0(V |\sketch(V)=ss^*) \le (\gamma -t+1 )|\mathbb{F}|$.  Averaging over $\sketch(V)=ss^*$ one has that $\tilde{H}_0(V|\sketch(V)) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
\end{proof}
\bnote{the reviewer is complaining that $V | \sketch(V)$ is not a distribution.  don't know why}
\begin{lemma}
\label{lem:side info determines sketch}
$\Hav(V | \sketch(V), Z) <2$.
\end{lemma}
\begin{proof}
Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
 As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.  %Having seen $V$ there are many possible values for $Z$.  Furthermore, the distributions $V|Z$ have disjoint support outside of the observed point.  
 The only information seen by $\sketch$ algorithm is in the point $V=v$.  The length of this point is $|\mathbb{F}|^\gamma$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
 \[
 \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}}{|\mathbb{F}|^\gamma}\right) = \log \left( (|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|\right).
 \]
Consider two possible $z_1, z_2$ that are possible values of $Z$~(having seen $v$).  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).

@@

\lnote{this lemma should probably live elsewhere since it is also needed for the FE case}
\bnote{fine with it being here as the FE case lives in the appendix too}
\begin{lemma}
\label{lem:log-minus-one}
For any real numbers $\alpha \leq \eta$ with $\eta \ge e+1$ (in particular, $\eta\ge 4$ suffices), the following holds:
$\alpha \log (\eta-1) > (\alpha-1)\log \eta$. 
\end{lemma}

@@

Consider some $p^*\in A_{p}$.  
The distribution $\Key|P=p^*$ is the set of possible keys.
The distribution $\Key|P=p^*$ induces a partition on the metric space.  That is, for every $w\in\mathcal{M}$, there exists a unique value $\key$ such that $\rep(w, p^*) =\key$.  Denote this partition by $Q_{p^*,\key} = \{w | \rep(w, p^*) = \key\}$.

>>>>

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$ where $n =\log \M$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = \beta_{t,i} /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, \{W\}, \tilde{m}, t)$-known distribution secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 4$.

@@

\begin{proof}
We prove the stronger average case statement.
We first describe a family $\mathcal{W}_Z$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
Let $\mathcal{W}_Z$ be the set of all distributions of the form 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} w_1 + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{\gamma} \end{pmatrix} 
\]
The family is defined by the parameters $a_2,.., a_\gamma$ and $b_2,..., b_\gamma$ (seen by the adversary) for arbitrary $b_i$ and $a_i\neq 0$.  The outcome $w\leftarrow W_z$ is sampled by sampling $w_1$ and computing $w$.  Each distribution $W_z$ is an affine line in space $\mathbb{F}^\gamma$. The algorithm $\sketch, \rec$ never see $Z$ only the outcome of $v\leftarrow V$.
Fix some $4\le t < \gamma$.
We show the following~(in \apref{sec:proof secure sketch imposs}):

@@

Our counterexample uses a slightly different family of distributions $\mathcal{W}_Z$ than the counterexample for secure sketches.  
We will work over a binary alphabet~(we used a large alphabet in our counterexample for secure sketches).  A  property of the binary Hamming space is that a large fraction of any set of bounded size is the near ``boundary'' of that set.  This will be crucial in our proof.  We will embed the larger alphabet in the secure sketch counterexample into the binary Hamming metric.
Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} .
\]
The multiplication is in $\mathbb{F}$.  The family $\mathcal{W}_Z$ is parameterized by $z = a_2,..., a_{n/\nu}, b_2,..., b_{n/\nu}$ for arbitrary $b_i$ and $a_i\neq 0$.  
A particular distribution $W_z$ is the uniform distribution over choices of $x$.
 Define $V$ as the process of uniformly choosing $W_z\leftarrow \mathcal{W}_Z$ and then sampling from $w\leftarrow W_z$.  The adversary sees $\sketch(V)$  and $Z$.  We then show the following~(proofs in \apref{sec:fuzz ext proof}):
\begin{itemize}
\item \propref{prop:dist fuzzy ent fuzz}: for all $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z) = \omega (\log n)$. 
\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
\item \lemref{lem:fuzz can't get key}: In expectation across $Z$, a large subset of keys that are not possible.  In more detail,
\begin{itemize}
\item Half the keys have at most $2^{n- \kappa}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $\Key_{small}$.  
\item Consider some $\key \in \Key_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
Consider the set of $V_{\key } = \{w | \rep(w, p) = \key \}$.  All points in $V | \sketch(V)$ are distance $t$ from a boundary of $V_\key$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $\key$).  We show that most of $V_\key$ is near a boundary.  A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short}.  Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.  The number of $w$ that could produce $\key$ is small.
\item There are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).  Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_2$ have disjoint support outside of a single point $w$.
\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ contains at most one point~(the received point $v$).  Checking if $V|Z \cap V_{\key}$ is nonempty is an effective distinguisher.
\end{itemize}
\end{itemize}

@@

\section{A Definitional Equivalence}
\label{sec:def equiv}

As described in \secref{sec:family of dist}, our negative results rule out security for an average member of $\mathcal{W}_Z$.  It may be possible to significantly improve parameters by only ruling out security for a single member $W_z$.

Recall the security game of a fuzzy extractor: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W_z\in \mathcal{W}_Z$ 3) The challenger wins if $\Hav(W_z|\sketch(W_z))\ge \tilde{m}$.  Instead of just thinking of the uniform distribution over $\mathcal{W}_Z$, consider an arbitrary distribution $V$ over elements of $\mathcal{W}_Z$.  The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie} if $\mathcal{A}$ announces $V$ instead of a single element $W_z$.  That is, the following two player games have the same equilibrium:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{W}_Z}_1(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W}_Z)$\\
$W_z \leftarrow \mathcal{A}(\mathcal{W}, \sketch, \rec)$\\
If $W_z\not\in \mathcal{W}_Z$, $\mathcal{C}$ wins.\\
If $\Hav(W_z | \sketch(W_z))\ge \tilde{m}$, $\mathcal{C}$ wins.\\
Else $\mathcal{A}$ wins.
\end{tabbing} 
\vspace{.065in}
\end{minipage}  &
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{W}_Z}_2(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
$V \leftarrow \mathcal{A}(\mathcal{W}_Z)$\\
$(\sketch, \rec)\leftarrow \mathcal{C}(V, \mathcal{W}_Z)$\\
$W_z \leftarrow V$\\
If $\Hav(W_z | \sketch(W_z))\ge \tilde{m}$, $\mathcal{C}$ wins.\\
Else $\mathcal{A}$ wins.
\end{tabbing}
\end{minipage}
\end{tabular}
\end{center}

\noindent
This means that showing security for a family of distributions $\mathcal{W}_Z$ is equivalent to showing security for all distributions $V$ when the distribution is known to the algorithms $(\sketch, \rec)$.  In our negative results, the adversary uses the uniform distribution over $\mathcal{W}_Z$.  However, it may be possible to improve parameters by using a different $V$.

\section{Fuzzy min-entropy}
\label{sec:proof fuzz necessary}
In this section, we provide proofs of statements in \secref{sec:minimal conditions}.  
\begin{proof}[Proof of \propref{prop:fuzz necessary}]
Let $W$ be a distribution where $\Hfuzz(W) = m$.  This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] = 2^{-m}$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $\key, p$.
\item If $\rep(w', p) = \key$, output $1$.
\item Else output $0$.
\end{itemize}
Clearly, $\Pr[D(\Key, P) = 1]\geq 2^{-m} - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus,
\[
\sd((\Key, P), (U_\kappa, P)) \ge \delta^D((\Key, P), (U_\kappa, P))\geq 2^{-m} -\delta -2^{-\kappa}.
\]
This completes the proof of \propref{prop:fuzz necessary}.
\end{proof}
\begin{proof}[Proof of \lemref{lem:conditional fuzz rule}]
\begin{align*}
\Hfuzz(W | P=p) &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \Pr[W=w | P=p] \right)\\
 &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w \wedge P=p]}{\Pr[P=p]} \right)\\
% &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
 &\ge -\log \left(\max_{w'}  \sum_{w\in W| \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
 &= \Hfuzz(W) + \log \Pr[P=p].
\end{align*}
This completes the proof of \lemref{lem:conditional fuzz rule}.
\end{proof}

@@

Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.  The size of $W^*$ is at most $\beta_{t,i}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  The probability that another element $w^*$ matches the hash is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{\beta_{t,i}-1}{|R_i|}\le \frac{\beta_{t, i}}{|R_i|} = \delta
\end{align*}
The first inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.

@@

\begin{proposition} 
\label{prop:each element good} For each $W_z\in\mathcal{W}_Z$, $\Hfuzz(W_z) = \omega(\log n)$.
\end{proposition}
\begin{proof}
Consider some $W_z\in\mathcal{W}_Z$.  The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W_z) \ge \omega(\log n)$.  We now show that for any $w, w'\in W_z$, $\dis(w, w') = \gamma>t$.  This shows that $\Hfuzz(W_z) = \Hoo(W_z)$.  Fix some $w, w'\in W_z$.  Clearly, $w_1 \neq w_1'$, for any $i$, $w_i = a_i w_1 + b_i$ and $w_i' = a_i w_1' + b_i$.  Since $a_i\neq 0$, $a_iw_1 \neq a_iw_1'$ and thus $a_iw_1+b_i \neq a_iw_1'+b_i$.  That is, $\dis (w, w')  =\gamma$.
\end{proof}

\begin{proposition}
\label{prop:distribution uniform} $V$ is the uniform distribution over $\mathbb{F}^\gamma$.
\end{proposition}
\begin{proof}
Consider some $w\in V$.  Then $w$ was drawn from an intermediate distribution $W_z$ with coefficients $a_2, b_2, ..., a_\gamma , b_\gamma$.  The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\gamma$ are uniformly distributed.
\end{proof}

@@

By the Singleton bound, this implies that $H_0(V |\sketch(V)=ss^*) \le (\gamma -t+1 )|\mathbb{F}|$.  Averaging over $\sketch(V)=ss^*$ one has that $\tilde{H}_0(V|\sketch(V)) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
\end{proof}
\bnote{the reviewer is complaining that $V | \sketch(V)$ is not a distribution.  don't know why}
\begin{lemma}
\label{lem:side info determines sketch}
$\Hav(V | \sketch(V), Z) <2$.
\end{lemma}
\begin{proof}
Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
 As described above, the view of $\sketch, \rec$ is a uniform distribution $V$. 
The length of this point is $|\mathbb{F}|^\gamma$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
 \[
 \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}}{|\mathbb{F}|^\gamma}\right) = \log \left( (|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|\right).
 \]
Consider two possible $z_1, z_2$ that are possible values of $Z$~(having seen $v$).  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).

@@

\begin{lemma}
\label{lem:log-minus-one}
For any real numbers $\alpha \leq \eta$ with $\eta \ge e+1$ (in particular, $\eta\ge 4$ suffices), the following holds:
$\alpha \log (\eta-1) > (\alpha-1)\log \eta$. 
\end{lemma}

@@

Consider some $p^*\in A_{\epsilon}$.  
The distribution $\Key|P=p^*$ is the set of possible keys.
The distribution $\Key|P=p^*$ induces a partition on the metric space.  That is, for every $w\in\mathcal{M}$, there exists a unique value $\key$ such that $\rep(w, p^*) =\key$.  Denote this partition by $Q_{p^*,\key} = \{w | \rep(w, p^*) = \key\}$.
